surfing

### 2021-05-12 inst/surfing.Rmd
do not include QS surfers

```{r}
surfing_table <- read.table("wct_surfers_table.txt",header=TRUE)
options(width=100)
surfing_table
wildcards <- rownames(surfing_table)[-(1:36)]
wildcards
```

@@

```{r definesurfing, cache=TRUE}
remove <- c(wildcards, "Vries")
surfing <- hyper2()
for(v in o){
   r <- v[-1]  # first entry is venue
   numberretained <- sum(!(r %in% remove))
   if(numberretained > 1){
     r <- r[!(r %in% remove)]
     surfing <- surfing + race(r)
    }
}	
summary(surfing)
```

@@

```{r directlogplotofstrenghts}
jjO <- surfing_table$points[1:36]
names(jjO) <- rownames(surfing_table)[1:36]
jjL <- surfing_maxp
jjO <- ordertrans(jjO)
jjL <- ordertrans(jjL)
plot(jjO,jjL,pch=16,log='xy')
fit <- lm(log10(jjL)~log10(jjO))
for(i in seq_along(jjO)){
text(jjO[i],jjL[i],names(jjL)[i],col='gray',pos=4,cex=0.5)
}
abline(fit)
```

@@

```{r ordertransplotplot,fig.cap="Official ranks vs likelihood rank, WCT"}
rL <- sort(surfing_maxp,decreasing=TRUE)
rL[] <- seq_along(rL)    # likelihood-based rank
rO <- seq_len(nrow(surfing_table))[1:36]
names(rO) <- rownames(surfing_table)[1:36]
rO
rL
sort(names(rO))
sort(names(rO))
sort(names(rO))==sort(names(rO))
ordertransplot(rO,rL,xlab="offical rank",ylab="likelihood rank",main="WCT 2019")
```

>>>>

```{r}
surfing_table <- read.table("wct_surfers_table.txt",header=TRUE)
options(width=100)
surfing_table
wildcards <- rownames(surfing_table)[-(1:36)]
wildcards
QS <- rownames(surfing_table)[c(23:33,35:36)]
QS
```

@@

```{r definesurfing, cache=TRUE}
remove <- c(wildcards, QS, "Vries")
wanted <- which(!(rownames(surfing_table) %in% remove)) # used at directlogplotofstrengths
surfing <- hyper2()
for(v in o){
   r <- v[-1]  # first entry is venue
   numberretained <- sum(!(r %in% remove))
   if(numberretained > 1){
     r <- r[!(r %in% remove)]
     surfing <- surfing + race(r)
    }
}	
summary(surfing)
```

@@

```{r directlogplotofstrenghts}
jjO <- surfing_table$points[wanted]
names(jjO) <- rownames(surfing_table)[wanted]
jjL <- surfing_maxp
jjO <- ordertrans(jjO)
jjL <- ordertrans(jjL)
plot(jjO,jjL,pch=16,log='xy')
fit <- lm(log10(jjL)~log10(jjO))
for(i in seq_along(jjO)){
text(jjO[i],jjL[i],names(jjL)[i],col='gray',pos=4,cex=0.5)
}
abline(fit)
```

@@

```{r ordertransplotplot,fig.cap="Official ranks vs likelihood rank, WCT"}
rL <- sort(surfing_maxp,decreasing=TRUE)
rL[] <- seq_along(rL)    # likelihood-based rank
rO <- seq_len(nrow(surfing_table))[wanted]
names(rO) <- rownames(surfing_table)[wanted]
rO
rL
sort(names(rO))
sort(names(rO))
sort(names(rO))==sort(names(rO))
ordertransplot(rO,rL,xlab="offical rank",ylab="likelihood rank",main="WCT 2019")
```
